%-------------------------
% Resume in Latex
% Author : Deepanjan Kowar
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/deepanjank/}{\Large Deepanjan Kowar}} & Email : \href{mailto:deepanjan.kowar@gmail.com}{deepanjan.kowar@gmail.com}\\
  \href{https://www.linkedin.com/in/deepanjank/}{www.linkedin.com/in/deepanjank/} & Mobile : +91-78288-05543 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Bangalore}{}
      {Master of Technology in Information Technology | CGPA: 3.47/4}{July 2017 -- July 2019}
    \resumeSubheading
      {Bhilai Institute of Technology, Durg}{}
      {Bachelor of Engineering in Computer Science and Engineering | CGPA: 9.07/10}{Aug. 2013 -- July 2017}
    \resumeSubheading
      {Delhi Public School, Bhilai}{}
      {12\textsuperscript{th} Grade | 91.2\%}{2013}
    \resumeSubheading
      {Delhi Public School, Durg}{}
      {10\textsuperscript{}{th} Grade | CGPA: 10/10}{2011}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Morgan Stanley}{Bangalore, India}
      {Spring Intern}{January 2019 - Present}
      \resumeItemListStart
        \resumeItem{POC}
          {Working on a project, which deals with building a textual summary around structured data using NLG.}
    \resumeItemListEnd
      
    \resumeSubheading
      {ClearTax}{Bangalore, India}
      {Software Engineering Intern}{May 2018 - July 2018}
      \resumeItemListStart
        \resumeItem{Tax Filing}
          {Worked as a back-end engineer in the Filing team of ClearTax, contributing to various feature additions and bug fixes. Developed a system for Form-16 parsing.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Twitter Data Summarization}
      {Graph-based approach for summarizing tweets. Where a graph is first constructed considering the similarity among tweets, and community detection techniques are then used on the graph to cluster similar tweets. Finally, a representative tweet is chosen from each cluster to be included into the summary.}
    \resumeSubItem{User Engagement}
      {Worked on development of user engagement model for VideoKen, a learning platform. Goal of the project is to classify users based on their engagement type with the platform and sending relevant nudges to the users so as to increase the engagement with the platform.
      }
    \resumeSubItem{Safe Navigation}
      {Application that is not only capable of suggesting the fastest but also the safest route based on accident and crime data.}
  \resumeSubHeadingListEnd

%-----------SKILLS------------------
\section{Software Proficiency}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {C, C++, R, Java, C\#, Javascript, SQL, PHP, bash}
    \resumeSubItem{Tools and Technologies}
      {R Studio, Eclipse, Visual Studio, NetBeans, .NET Framework, MVC, Arria Studio}
    \resumeSubItem{Areas of Interest}
      {Data Structures and Algorithms, Natural Language Processing}
  \resumeSubHeadingListEnd
  

%--------INDUSTRIAL TRAININGS----------
\section{Industrial Trainings}
\resumeSubHeadingListStart
    \itemsep-0.25em 
    \item{
      \textbf{Internet \& Web Technologies}{ | Perpetual Infotech, Pune | July 2016 }
    }
    \item{
      \textbf{Linux Server Networking \& Administration}{ | Rooman Technologies, Bangalore | July 2015}
    }
  \resumeSubHeadingListEnd


%----------ACHIEVEMENTS--------------
\section{Achievements}
\resumeSubHeadingListStart
    \itemsep-0.25em 
    \item{
      Secured \textbf{AIR 993} in \textbf{GATE 2017}.
    }
    \item {
        Secured \textbf{207\textsuperscript{th}} rank in \textbf{ACM ICPC 2018}, Amritapuri regional.
    }
    \item {
        \textbf{1\textsuperscript{st} Runner Up} in \textbf{Tesco Codeathon 2018}.
    }
    \item{
      \textbf{Certification (Elite)} on Introduction to Programming in C with a score of 83\% by \textbf{IIT Kanpur}.
    }
    \item{
        Training on \textbf{LINUX} conducted by \textbf{IIT Bombay} followed by \textbf{Virtual Hosting} project.
    }
  \resumeSubHeadingListEnd
%-------------------OTHERS-------------------
\section{Others}
\resumeSubHeadingListStart
    \itemsep-0.25em 
    \item{
        \textbf{Teaching Assistant} at \textbf{InterviewBit}, a platform to learn skills that you need for technology jobs.
    }
    \item{
      Manager and trainer of \textbf{Clicks Photography Club}, consisting of more than 100 members,which aims at promoting and educating photography and its various aspects.
    }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}