%-------------------------
% Resume in Latex
% Author : Deepanjan Kowar
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/deepanjank/}{\Large Deepanjan Kowar}} & Email : \href{mailto:deepanjan.kowar@gmail.com}{deepanjan.kowar@gmail.com}\\
  \href{https://www.linkedin.com/in/deepanjank/}{www.linkedin.com/in/deepanjank/} & Mobile : +91-78288-05543 \\
\end{tabular*}


%-----------OBJECTIVE-----------------
\section{Carrer Objective}
Intend to build a career with leading corporate of hi-tech environment with committed \& dedicated people, which will help me to explore myself fully and realize my potential.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology, Bangalore}{}
      {Master of Technology in Information Technology | CGPA: 3.4/4}{July 2017 -- July 2019}
    \resumeSubheading
      {Bhilai Institute of Technology, Durg}{}
      {Bachelor of Engineering in Computer Science and Engineering | CGPA: 9.07/10}{Aug. 2013 -- July 2017}
    \resumeSubheading
      {Delhi Public School, Bhilai}{}
      {12\textsuperscript{th} Grade | 91.2\%}{2013}
    \resumeSubheading
      {Delhi Public School, Durg}{}
      {10\textsuperscript{}{th} Grade | CGPA: 10/10}{2011}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ClearTax}{Bangalore, India}
      {Software Engineering Intern}{May 2018 - Present}
      \resumeItemListStart
        \resumeItem{Tax Filing}
          {Working as a back-end engineer in the Filing team of ClearTax. Contributing to various feature additions and bug fixes.}
        \resumeItem{Form-16 Parsing}
          {Managing Form-16 parsing for the current tax season. This feature allow the users to file their tax returns effortlessly by simply uploading their Form 16 PDF.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------SKILLS------------------
\section{Software Proficiency}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {C, C++, R, Java, C\#, Javascript, SQL, PHP, bash}
    \resumeSubItem{Tools and Technologies}
      {R Studio, Eclipse, Visual Studio, NetBeans, .NET Framework, MVC}
    \resumeSubItem{Areas of Interest}
      {Algorithms, Natural Language Processing, Geographic Information Systems}
  \resumeSubHeadingListEnd
  
  
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Twitter Data Summarization}
      {Graph-based approach for summarizing tweets, by clustering tweets using community detection techniques and selecting representative tweets to be included into the summary.}
    \resumeSubItem{Safe Navigation}
      {Application that is not only capable of suggesting the fastest but also the safest route based on accident and crime data.}
    \resumeSubItem{Tiny URL}
      {Highly scalable URL shortening web service, which provides short aliases for redirection of long URLs.}
    \resumeSubItem{Payroll Management System}
      {For automating salary system for an organization. Calculates and stores monthly salaries, tax of employees and generates salary slips.}
  \resumeSubHeadingListEnd



%--------INDUSTRIAL TRAININGS----------
\section{Industrial Trainings}
\resumeSubHeadingListStart
    \itemsep-0.25em 
    \item{
      \textbf{Internet \& Web Technologies}{ | Perpetual Infotech, Pune | July 2016 }
    }
    \item{
      \textbf{Linux Server Networking \& Administration}{ | Rooman Technologies, Bangalore | July 2015}
    }
  \resumeSubHeadingListEnd


%----------ACHIEVEMENTS--------------
\section{Achievements}
\resumeSubHeadingListStart
    \itemsep-0.25em 
    \item{
      Secured \textbf{AIR 993} in \textbf{GATE 2017}.
    }
    
    \item{
      \textbf{Certification (Elite)} on Introduction to Programming in C with a score of 83\% by \textbf{IIT Kanpur}.
    }
    \item{
        Training on \textbf{LINUX} conducted by {IIT Bombay} followed by \textbf{Virtual Hosting} project.
    }
    \item{
        Participated in \textbf{BITCON} a National Conference on \textbf{“Innovations in Computation, Communication \& Cybernetics”}.
    }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}